\textls[-0]{\thetitle}

### 2023-03-15 metatheory-condensed.tex
add a comment from Zhixuan

W-types~\cite{martin1984intuitionistic} are a succinct way to model
inductive types in MLTT.
Together with the identity type, they can express a
whole host of inductive types~\cite{hugunin2021not}.
%
In our formulation, a W-type is given by a W-type signature $\goodWSig{\Gm}{\wsig}{n}$ 
composed of $n$ pairs of types (\ruleref{wsig/empty} and \ruleref{wsig/add}).
%
Each pair models a constructor of the inductive type.
The $i$-th pair, projected from the signature~$\wsig$ using the forms
$\goodType{\Gm}{\wsigproj{i}{1}{\wsig}}{}$ and
$\goodType{\Gm,x : \wsigproj{i}{1}{\wsig}}{\wsigproj{i}{2}{\wsig}}{}$,
defines the $i$-th constructor.
That is, given two arguments $\goodTerm{\Gm}{t_1}{\wsigproj{i}{1}{\wsig}}$ and
$\goodTerm{\Gm, x : \nsub{\wsigproj{i}{2}{\wsig}}{x}{t_1}}{t_2}{\El{\wcode{\wsig}}}$,
we can construct a term $\Wsup{i}{\wsig}{t_1}{x.t_2}$ of the W-type (\ruleref{tm/wsup}).
$\wcode{\wsig}$ gives the code of the
W-type (\ruleref{tm/w}).

>>>>

W-types~\cite{martin1984intuitionistic} are a succinct way to model
inductive types in MLTT.
Together with the identity type, they can express a
whole host of inductive types~\cite{hugunin2021not}.
%
In our formulation, a W-type is given by a W-type signature $\goodWSig{\Gm}{\wsig}{n}$ 
composed of $n$ pairs of types (\ruleref{wsig/empty} and \ruleref{wsig/add}).\Zhixuan{Page 14: I don't see the necessity of introducing "enhanced W-types". Since there are already boolean types and Σ types, Fin types can be defined. Using Fin, ordinary W types suffice to define trees with n constructors. So it might be clearer to just define 'enhanced W-types' as syntactic sugar.}\YZreply{I concur.}
%
Each pair models a constructor of the inductive type.
The $i$-th pair, projected from the signature~$\wsig$ using the forms
$\goodType{\Gm}{\wsigproj{i}{1}{\wsig}}{}$ and
$\goodType{\Gm,x : \wsigproj{i}{1}{\wsig}}{\wsigproj{i}{2}{\wsig}}{}$,
defines the $i$-th constructor.
That is, given two arguments $\goodTerm{\Gm}{t_1}{\wsigproj{i}{1}{\wsig}}$ and
$\goodTerm{\Gm, x : \nsub{\wsigproj{i}{2}{\wsig}}{x}{t_1}}{t_2}{\El{\wcode{\wsig}}}$,
we can construct a term $\Wsup{i}{\wsig}{t_1}{x.t_2}$ of the W-type (\ruleref{tm/wsup}).
$\wcode{\wsig}$ gives the code of the
W-type (\ruleref{tm/w}).
